Scientific Reports Title to see here (20 words or less)

### 2016-06-24 draft1.tex
added some new information to intro

              
\documentclass[fleqn,10pt]{wlscirep}
\title{Scientific Reports Title to see here (20 words or less)}
\author[1]{Rachel LeCover}
\author[1,*]{Jeffrey D. Varner}
\affil[1]{Affiliation, School of Chemical and Biomolecular Engineering, Ithaca NY, 14852, USA}
\affil[*]{jdv27@cornell.edu}
%\keywords{Keyword1, Keyword2, Keyword3}
\begin{abstract}
Example Abstract. Abstract must be under 200 words and not include subheadings or citations. Example Abstract. Abstract must be under 200 words and not include subheadings or citations. Example Abstract. Abstract must be under 200 words and not include subheadings or citations. Example Abstract. Abstract must be under 200 words and not include subheadings or citations. Example Abstract. Abstract must be under 200 words and not include subheadings or citations. Example Abstract. Abstract must be under 200 words and not include subheadings or citations. Example Abstract. Abstract must be under 200 words and not include subheadings or citations. Example Abstract. Abstract must be under 200 words and not include subheadings or citations. 
\end{abstract}
\begin{document}
\flushbottom
\maketitle
% * <john.hammersley@gmail.com> 2015-02-09T12:07:31.197Z:
%
%  Click the title above to edit the author information and abstract
%
\thispagestyle{empty}
\noindent Please note: Abbreviations should be introduced at the first mention in the main text – no abbreviations lists. Suggested structure of main text (not enforced) is provided below.
\section*{Introduction}
The rate at which a heart beats is determined, in part, by the sympathetic and parasympathetic portions of the nervous system. When the sympathetic nervous system is stimulated, it releases epinephrine and norepinephrine  which increase heart rate. The parasympathetic system releases acetylcholine which decreases heart rate.  These two systems, often described as an accelerator and a brake, are not totally independent on each other, rather, they interact through second messengers cAMP and cGMP. \cite{olshansky2008parasympathetic}
Heart rate is also controlled by the baroreflex system. The baroreflex system consists of baroreceptors, tension sensitive nerve endings found in the circulatory system. \cite{ottesen1997modelling} When they sense a change in pressure, they cause a change in the frequency of nerve activity. When pressure (and stretch) rapidly increase, so does the baroreceptor firing rate. \cite{negative1999reflexes} This effects of this signal are not instantaneous, rather, there is a time delay on the order of seconds before the sympathetic and parasympathetic nervous systems respond. \cite{ottesen1997modelling}

>>>>

              
\documentclass[fleqn,10pt]{wlscirep}
\title{Scientific Reports Title to see here (20 words or less)}
\author[1]{Rachel LeCover}
\author[1,*]{Jeffrey D. Varner}
\affil[1]{Affiliation, School of Chemical and Biomolecular Engineering, Ithaca NY, 14852, USA}
\affil[*]{jdv27@cornell.edu}
%\keywords{Keyword1, Keyword2, Keyword3}
\begin{abstract}
Example Abstract. Abstract must be under 200 words and not include subheadings or citations. Example Abstract. Abstract must be under 200 words and not include subheadings or citations. Example Abstract. Abstract must be under 200 words and not include subheadings or citations. Example Abstract. Abstract must be under 200 words and not include subheadings or citations. Example Abstract. Abstract must be under 200 words and not include subheadings or citations. Example Abstract. Abstract must be under 200 words and not include subheadings or citations. Example Abstract. Abstract must be under 200 words and not include subheadings or citations. Example Abstract. Abstract must be under 200 words and not include subheadings or citations. 
\end{abstract}
\begin{document}
\flushbottom
\maketitle
% * <john.hammersley@gmail.com> 2015-02-09T12:07:31.197Z:
%
%  Click the title above to edit the author information and abstract
%
\thispagestyle{empty}
\noindent Please note: Abbreviations should be introduced at the first mention in the main text – no abbreviations lists. Suggested structure of main text (not enforced) is provided below.
\section*{Introduction}
The rate at which a heart beats is determined, in part, by the sympathetic and parasympathetic portions of the nervous system. When the sympathetic nervous system is stimulated, it releases epinephrine and norepinephrine. Norepinephrine increases heart rate by increasing the rate of depolarization in pacemaker cells and increases contractability through the phosphorlation of several types of receptors.\cite{boron2016medical} The parasympathetic system releases acetylcholine which decreases heart rate and contractibility through its binding to M$_2$ receptors.  These two systems, often described as an accelerator and a brake, are not totally independent on each other, rather, they interact through second messengers cAMP and cGMP. \cite{olshansky2008parasympathetic}
Heart rate is also controlled by the baroreflex system. The baroreflex system consists of baroreceptors, tension sensitive nerve endings found in the circulatory system. \cite{ottesen1997modelling} When they sense a change in pressure, they cause a change in the frequency of nerve activity. When pressure (and stretch) rapidly increase, so does the baroreceptor firing rate. \cite{negative1999reflexes} This effects of this signal are not instantaneous, rather, there is a time delay on the order of seconds before the sympathetic and parasympathetic nervous systems respond. \cite{ottesen1997modelling}

This control process leads to a negative feedback loop, where if the mean arterial pressure increases, vasodilation and bradycardia occur, whereas if the mean arterial pressure decreases, the opposite, vasoconstriction and tachycardia occur. \cite{boron2016medical}
